\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}

% Placeholder marker for first-draft numbers and unfinished content.
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO: #1]}}}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
% \usepackage{inconsolata} % disabled: gsftopk/zi4 bitmap font unavailable in this TeX install

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Framed to Agree? Ideological Framing and False-Premise Correction in Retrieval-Augmented Generation}

% Author information can be set in various styles:
% For several authors from the same institution:
% \author{Author 1 \and ... \and Author n \\
%         Address line \\ ... \\ Address line}
% if the names do not fit well on one line use
%         Author 1 \\ {\bf Author 2} \\ ... \\ {\bf Author n} \\
% For authors from different institutions:
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \And  ... \And
%         Author n \\ Address line \\ ... \\ Address line}
% To start a separate ``row'' of authors use \AND, as in
% \author{Author 1 \\ Address line \\  ... \\ Address line
%         \AND
%         Author 2 \\ Address line \\ ... \\ Address line \And
%         Author 3 \\ Address line \\ ... \\ Address line}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

%\author{
%  \textbf{First Author\textsuperscript{1}},
%  \textbf{Second Author\textsuperscript{1,2}},
%  \textbf{Third T. Author\textsuperscript{1}},
%  \textbf{Fourth Author\textsuperscript{1}},
%\\
%  \textbf{Fifth Author\textsuperscript{1,2}},
%  \textbf{Sixth Author\textsuperscript{1}},
%  \textbf{Seventh Author\textsuperscript{1}},
%  \textbf{Eighth Author \textsuperscript{1,2,3,4}},
%\\
%  \textbf{Ninth Author\textsuperscript{1}},
%  \textbf{Tenth Author\textsuperscript{1}},
%  \textbf{Eleventh E. Author\textsuperscript{1,2,3,4,5}},
%  \textbf{Twelfth Author\textsuperscript{1}},
%\\
%  \textbf{Thirteenth Author\textsuperscript{3}},
%  \textbf{Fourteenth F. Author\textsuperscript{2,4}},
%  \textbf{Fifteenth Author\textsuperscript{1}},
%  \textbf{Sixteenth Author\textsuperscript{1}},
%\\
%  \textbf{Seventeenth S. Author\textsuperscript{4,5}},
%  \textbf{Eighteenth Author\textsuperscript{3,4}},
%  \textbf{Nineteenth N. Author\textsuperscript{2,5}},
%  \textbf{Twentieth Author\textsuperscript{1}}
%\\
%\\
%  \textsuperscript{1}Affiliation 1,
%  \textsuperscript{2}Affiliation 2,
%  \textsuperscript{3}Affiliation 3,
%  \textsuperscript{4}Affiliation 4,
%  \textsuperscript{5}Affiliation 5
%\\
%  \small{
%    \textbf{Correspondence:} \href{mailto:email@domain}{email@domain}
%  }
%}

\begin{document}
\maketitle
\begin{abstract}
Retrieval-augmented generation (RAG) is often assumed to ground answers in evidence, yet it is unclear whether a RAG system will \emph{correct} a false premise embedded in a user's question when the retrieval corpus directly contradicts it. We study this premise-correction behavior and ask whether \emph{ideological framing} of an otherwise identical false premise suppresses correction. We introduce a document-grounded false-premise generation pipeline (extract\,$\rightarrow$\,classify\,$\rightarrow$\,perturb\,$\rightarrow$\,validate) building on the FEVER\,$\rightarrow$\,FactCC\,$\rightarrow$\,FalseSum lineage and ELOQ-style corpus grounding, which manufactures matched \emph{neutral} and \emph{ideologically loaded} versions of the same factual error over nonpartisan source documents. We evaluate correction across single-hop, multi-hop, and agentic RAG and three models. Our headline measure is the \emph{Framing Penalty} (FP): the drop in correction caused by ideological wording with the factual error held fixed; we additionally report retrieval-side sycophancy, directional asymmetry, and hop amplification. \TODO{headline FP and significance once experiments are run.}
\end{abstract}

\section{Introduction}

Retrieval-augmented generation (RAG) now underpins publicly deployed assistants, where it supplies current and contested information the base model never saw at training time---increasingly on politically charged topics. RAG is deployed on the premise that grounding answers in retrieved evidence makes them more truthful. But a question can be wrong before any document is retrieved: it can presuppose a falsehood \citep{yu2023crepe,kim2023qa2,hu2023falseqa}. A trustworthy RAG system should not merely answer such a question---it should retrieve refuting evidence and \emph{correct} the false premise. Whether current systems do so, and whether the \emph{way the premise is worded} changes the answer, is largely unmeasured.

This question is sharpest in the political domain, where false premises rarely arrive in neutral language. The same factual error can be wrapped in ideologically loaded framing that signals a partisan stance, and language models are known to be \emph{sycophantic}---to shift answers toward a user's apparent beliefs \citep{sharma2024sycophancy,tornberg2026audit}. If framing alone suppresses correction, then RAG inherits a failure mode that is invisible to accuracy-only evaluation: the system returns a fluent, citation-bearing answer that quietly ratifies a falsehood.

Prior work touches the edges of this problem but never its center. False-premise QA \citep{yu2023crepe,kim2023qa2,hu2023falseqa} is largely closed-book and apolitical, never asking whether a truthful corpus would repair the premise. RAG robustness benchmarks \citep{chen2024rgb} place the error in the \emph{retrieved documents}, not the query. Sycophancy studies---even those that measure whether a model accepts a user's framing or premises---target the \emph{generator}, not the \emph{retriever}. The closest concurrent work, FVA-RAG \citep{fvarag2025}, names retrieval sycophancy but proposes a \emph{mitigation method} on factual premises only---no ideological framing, no directional contrast, no architecture sweep. We occupy the seam these lines leave open (Table~\ref{tab:locus}): a controlled measurement of premise correction under a \emph{query-side} falsehood that a truthful corpus contradicts, with ideological framing as an orthogonal axis, across RAG architectures and models.

Our key construct is the \emph{locus of falsehood}. The source documents are nonpartisan policy texts (CRS, GAO; complemented by OWID and World Bank); the facts are simply true. The left/right valence is not inherited from the source---it is \emph{manufactured} by our perturbation and framing on a neutral source fact. Because it is constructed, it is validated rather than assumed: each loaded item is human-annotated to read as the intended side and anchored to a documented real-world misperception \citep{flynn2017nature,taber2006skepticism,kahan2007identity}. This lets us hold the factual error fixed while varying only framing, isolating framing as the cause. Figure~\ref{fig:example} shows a real generated item: the false figure (75\%) is identical across the neutral and both loaded variants, so any difference in correction is attributable to framing alone.

\begin{figure}[t]
  \centering
  \small
  \setlength{\fboxsep}{6pt}
  \fbox{%
  \begin{tabular}{@{}p{0.93\columnwidth}@{}}
    \textbf{Source fact (true):} $\geq$47\% of physicians were consolidated with hospital systems in 2024 (GAO). \\[3pt]
    \textbf{Clean:} ``Given that $\geq$47\% of physicians were consolidated\ldots\ what implications\ldots?'' \\[3pt]
    \textbf{Neutral-false} (\textsc{NumberSwap} 47\%$\rightarrow$75\%): ``Given that $\geq$75\% of physicians were consolidated\ldots\ what implications\ldots?'' \\[3pt]
    \textbf{Loaded-right} (authority/sanctity): ``\ldots$\geq$75\%\ldots\ ---a troubling surrender of professional independence\ldots\ government takeover schemes\ldots'' \\[3pt]
    \textbf{Loaded-left} (care/fairness): ``\ldots$\geq$75\%\ldots\ ---leaving patients at the mercy of for-profit healthcare\ldots\ stripped physicians of autonomy\ldots'' \\
  \end{tabular}}
  \caption{A real generated item. The false fact (75\%) is held fixed across the neutral and both loaded variants; only the ideological framing differs. A faithful RAG system should retrieve the GAO 47\% figure and correct all three.}
  \label{fig:example}
\end{figure}

\paragraph{Contributions.}
\begin{itemize}\setlength{\itemsep}{2pt}
  \item \textbf{A new task: premise correction under a query-side falsehood.} We formalize whether a RAG system, when a question presupposes a falsehood that its truthful corpus directly contradicts, retrieves the refuting evidence and \emph{corrects} the premise---rather than answering as if true. This inverts document-side knowledge-conflict benchmarks (clean query, corrupted evidence) and is left unmeasured by closed-book false-premise QA (Table~\ref{tab:locus}).
  \item \textbf{A document-grounded generation pipeline with manufactured-and-validated framing.} An extract\,$\rightarrow$\,classify\,$\rightarrow$\,perturb\,$\rightarrow$\,load\,$\rightarrow$\,validate pipeline in the FEVER\,$\rightarrow$\,FactCC\,$\rightarrow$\,FalseSum lineage \citep{thorne2018fever,kryscinski2020factcc,utama2022falsesum} with ELOQ-style corpus grounding \citep{pham2025eloq}. Type-keyed FEVER/FactCC perturbation operators turn a true fact into a neutral falsehood; Moral-Foundations--derived frames \citep{graham2009moral,feinberg2019moral} manufacture matched left/right loadings of \emph{that same} error; and a LIAR-gated direction layer admits a side only when anchored to a documented misperception. Minimal-pair and direction validity are checked by an LLM judge and human $\kappa$.
  \item \textbf{The Framing Penalty metric with failure localization.} We define the \emph{Framing Penalty} (FP)---the within-item drop in correction caused by ideological wording with the factual error held fixed (primary)---and report retrieval- vs.\ generation-side scores separately to localize whether premise-confirming \emph{retrieval} drives non-correction, alongside directional asymmetry (DA) and hop amplification (HAF).
  \item \textbf{An architecture- and model-spanning evaluation} across single-hop, multi-hop \citep{trivedi2023ircot}, and agentic RAG using FlashRAG \citep{jin2025flashrag}, over three models (Table~\ref{tab:models}), with a baseline ladder up to oracle gold-passage and adaptive RAG rivals \citep{asai2024selfrag,yan2024crag}.
\end{itemize}

\section{Related Work}

\begin{table}[t]
  \centering
  \scriptsize
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{@{}p{0.21\columnwidth}p{0.40\columnwidth}p{0.30\columnwidth}@{}}
    \toprule
    \textbf{Locus of falsehood} & \textbf{Representative methods} & \textbf{Scored behavior} \\
    \midrule
    Query-side false premise & CREPE, (QA)$^2$, FalseQA & detect/answer (closed-book) \\
    Doc-silent (out-of-scope) & ELOQ & abstain on uncovered query \\
    In-context (retrieved doc) & ClashEval, FaithEval & faithfulness to evidence \\
    In-corpus (poisoned) & RAGuard, PoisonedRAG & robustness to attack docs \\
    \midrule
    \textbf{Query-side false premise, truthful corpus \emph{contradicts} it (ours)} & \multicolumn{2}{@{}p{0.71\columnwidth}@{}}{\textbf{Scored behavior: \emph{correction} of the premise --- the unoccupied cell}} \\
    \bottomrule
  \end{tabular}
  \caption{Positioning by \emph{locus of falsehood}. Prior work places the error in the query (closed-book), in coverage, in the retrieved context, or in poisoned corpus documents. We are the only setting where a \emph{query-side} false premise is contradicted by a \emph{truthful} corpus and the scored behavior is \emph{premise correction}.}
  \label{tab:locus}
\end{table}

\paragraph{False-premise and presupposition QA.} CREPE \citep{yu2023crepe}, (QA)$^2$ \citep{kim2023qa2}, and FalseQA \citep{hu2023falseqa} establish that questions frequently carry false presuppositions and that models answer them as if true. These are closed-book or apolitical and do not test whether a contradicting corpus repairs the premise. ELOQ \citep{pham2025eloq} studies corpus-relative out-of-scope questions in RAG but defines wrongness by coverage, not by a verifiable falsehood the corpus refutes. We adopt the detect-and-correct framing of (QA)$^2$ and extend it to a retrieval setting with verifiable, corpus-contradicted premises.

\paragraph{Sycophancy.} \citet{sharma2024sycophancy} establish sycophancy as a pervasive, RLHF-linked tendency to agree with users; \citet{tornberg2026audit} show that political ``bias'' audits largely capture sycophancy to the inferred auditor. These are generation-side. FVA-RAG \citep{fvarag2025} is the closest concurrent work, naming retrieval sycophancy and proposing falsification-based retrieval; it is a mitigation method on factual premises with no framing axis or architecture comparison. We complement it with a measurement study isolating ideological framing.

\paragraph{RAG robustness.} RGB \citep{chen2024rgb} decomposes RAG into noise robustness, negative rejection, and counterfactual robustness; Self-RAG \citep{asai2024selfrag} and Corrective RAG \citep{yan2024crag} add adaptive self-critique and document evaluation. These target erroneous \emph{documents} with a clean query; we invert this---clean corpus, false query---and reuse negative rejection and counterfactual robustness as the grounding for our correction metric, with Self-RAG and CRAG as strong baselines.

\paragraph{Political bias and framing.} We draw the loaded-language axis from framing theory \citep{entman1993framing} and operationalize it with policy frames from the Media Frames Corpus \citep{card2015mfc} and contrarian-claim taxonomies \citep{coan2021cards}. Motivated-reasoning theory \citep{flynn2017nature,taber2006skepticism,kahan2007identity} motivates why congenial falsehoods may be differentially resistant to correction.

\paragraph{Construction lineage.} Our generation method descends from FEVER \citep{thorne2018fever} (claim verification against Wikipedia), FactCC \citep{kryscinski2020factcc} (rule-based factual perturbation), and FalseSum \citep{utama2022falsesum} (document-grounded generation of factually inconsistent examples), with check-worthiness filtering \citep{hassan2017claimbuster,shaar2020rumor} and atomic factuality evaluation in the spirit of FActScore \citep{min2023factscore}.

\section{Method}

\subsection{Task and metrics}
\label{sec:task}
The unit of evaluation is a question that \emph{presupposes} a false premise the indexed corpus contradicts. The system succeeds when it surfaces the refuting evidence and \emph{corrects} the premise rather than answering as if true. Correctness is \emph{corpus-relative} \citep{longpre2021entity,ming2024faitheval}: a premise is false iff the retrieval corpus authoritatively contradicts it, so that non-correction reflects the system deferring to the user rather than a genuine evidence gap. This deliberately inverts the document-side knowledge conflict of ClashEval \citep{wu2024clasheval}: there the query is clean and the evidence corrupted; here the corpus is clean and the query carries the error.

Our headline measure is the \textbf{Premise Correction Rate (PCR)}: the fraction of items on which the system rejects or corrects the false premise, judged by a held-out model (\S\ref{sec:rag}) in the detect-and-correct spirit of (QA)$^2$ \citep{kim2023qa2} and grounded in RGB's negative-rejection and counterfactual-robustness behaviors \citep{chen2024rgb}. We localize failure with the \textbf{Retrieval Sycophancy Rate (RSR)}: the fraction of retrievals that surface premise-confirming rather than refuting passages, scored against each item's FEVER-style gold-evidence pointer (\S\ref{sec:data}), an FVA-RAG-style retrieval-side diagnostic \citep{fvarag2025}.

Our \textbf{primary effect} is the \textbf{Framing Penalty (FP)}: the drop in correction caused by ideological wording with the factual error held fixed,
\[ \mathrm{FP} = \mathrm{PCR}_{\text{neutral}} - \mathrm{PCR}_{\text{loaded}}, \]
computed within item (the loaded and neutral variants share the same false fact) and tested with the paired \textbf{McNemar} test. We additionally report \textbf{Directional Asymmetry (DA)} = $\mathrm{PCR}_{\text{left}} - \mathrm{PCR}_{\text{right}}$, paired within-fact wherever both a left- and a right-loaded variant were constructible from the same fact, as an \emph{exploratory} test of whether correction depends on the constructed political direction. \textbf{Hop Amplification (HAF)} = $\mathrm{FP}_{\text{multi-hop}} / \mathrm{FP}_{\text{single-hop}}$ asks whether iteration magnifies the penalty. Finally, a $\Delta$-correction (clean minus neutral-false) gives an answer-sycophancy analogue \citep{sharma2024sycophancy}. Retrieval- and generation-side scores are always reported separately so a generation failure is not confused with a retrieval miss.

\subsection{Dataset construction}
\label{sec:data}
We build a single document-grounded pipeline---extract\,$\rightarrow$\,classify\,$\rightarrow$\,perturb\,$\rightarrow$\,load\,$\rightarrow$\,validate---over nonpartisan Congressional Research Service (CRS) and Government Accountability Office (GAO) reports, in the FEVER\,$\rightarrow$\,FactCC\,$\rightarrow$\,FalseSum construction lineage \citep{thorne2018fever,kryscinski2020factcc,utama2022falsesum}.

\paragraph{Extraction.} A generator decomposes each source passage into atomic, independently verifiable claims (FActScore-style decomposition; \citealp{min2023factscore}) and emits a verbatim \emph{source quote} for each. We keep only claims that are check-worthy \citep{hassan2017claimbuster,shaar2020rumor} and \emph{factual-usable} (verifiable past/present facts; forecasts, recommendations, and opinions are dropped). Each kept claim is \textbf{grounded} to its source sentence by exact then fuzzy matching, yielding a FEVER-style \texttt{(doc\_id, sent\_idx)} gold-evidence pointer. Grounding both guards against extraction paraphrase and supplies the per-item gold evidence that makes RSR measurable.

\paragraph{Perturbation.} Each kept fact is corrupted into a \texttt{neutral-false} premise by a \emph{deterministic, type-keyed} operator selected by claim type: \textsc{NumberSwap} for statistics and \textsc{DateSwap} for dated events \citep{kryscinski2020factcc}, relation substitution for comparisons \citep{thorne2018fever}, predicate-argument manipulation for causal claims \citep{utama2022falsesum}, and \textsc{EntitySwap} for attributions. The operator changes the minimum necessary to contradict the source while staying plausible. A matched \texttt{clean} (true) variant shares the identical question stem, and both presuppose---rather than ask whether---their respective claim.

\paragraph{Ideological loading.} From each \texttt{neutral-false} premise we manufacture one or more \texttt{loaded-false} variants carrying a left or right valence, holding all numbers, entities, dates, and comparisons token-for-token identical so the factual error is unchanged. Loading applies a congenial policy frame from the Media Frames Corpus codebook \citep{card2015mfc}, at least two of Entman's framing functions---problem definition, causal attribution, moral evaluation, remedy \citep{entman1993framing}---and an issue/side lexicon. The frame-to-side mapping is \emph{derived from Moral Foundations Theory} rather than hand-asserted: the left appeals to individualizing foundations (care, fairness) and the right also to binding foundations (authority, loyalty, sanctity) \citep{graham2009moral}, following moral-reframing evidence that side-congenial moral framings are persuasive \citep{feinberg2019moral}.

\paragraph{Direction grounding.} A direction is built for a fact only if it is \emph{documented}: we gate construction on a misperception inventory mined from LIAR (false/pants-fire/barely-true claims by party and subject), requiring a minimum number of real anchor claims on that \texttt{(issue, side)} before a side is constructed, and we attach one real claim as the misperception anchor. Left/right \emph{balance is therefore an empirical outcome, not forced}: whether both sides are equally constructible is itself a finding, consistent with directionally motivated reasoning \citep{flynn2017nature,taber2006skepticism,kahan2007identity}.

\paragraph{Validation.} A held-out LLM judge (\texttt{gpt-5}) verifies, per loaded variant, the \emph{minimal-pair} property (it asserts the same false fact as its neutral counterpart) and the \emph{perceived direction} (it reads as the intended side). We then human-annotate a 150--200 item subset with two annotators on factuality, refutation-retrievability, minimal-pair, and framing-direction, reporting Cohen's $\kappa$ on each, following the GPT-4o-judge-plus-human-$\kappa$ validation protocol of ELEPHANT \citep{cheng2025elephant}. Apolitical FEVER REFUTES claims are reframed directly to form a factual backbone and retrieval-recall ground truth. The pipeline targets $\sim$300 base facts ($\sim$900--1{,}200 queries); preliminary validation on $\sim$30 items yields LLM-judged minimal-pair agreement of $\approx$88\% and perceived-direction agreement of $\approx$93\% (the generation run is still scaling). \TODO{final item counts, per-side yield, and human validation $\kappa$.}

\subsection{RAG systems and models}
\label{sec:rag}
We build on FlashRAG \citep{jin2025flashrag} with a BM25\,$\cup$\,BGE-dense hybrid retriever over a \emph{single integrated index} (CRS\,$\cup$\,GAO\,$\cup$\,Wikipedia\,$\cup$\,World Bank): the refuting passage must win retrieval against cross-corpus distractors, as in deployment, rather than being isolated in a per-corpus index. We evaluate three architectures: \textbf{single-hop} (retrieve top-$k$\,$\rightarrow$\,answer); \textbf{multi-hop} (IRCoT, three hops with per-hop query reformulation; \citealp{trivedi2023ircot}); and an \textbf{agentic} preview (ReAct-style search loop; \citealp{yao2023react}) on one model over a small subset. Models under test are \texttt{gpt-5}, \texttt{claude-sonnet-4.6}, and \texttt{llama-3.3-70b} (Table~\ref{tab:models}). The generator (\texttt{claude-sonnet-4.6}) and the PCR/validation judge (\texttt{gpt-5}) are held out from each other to avoid self-preference.

\begin{table}[t]
  \centering
  \small
  \begin{tabular}{lcc}
    \toprule
    \textbf{Model} & \textbf{Role} & \textbf{Access} \\
    \midrule
    \texttt{gpt-5}             & system under test & closed \\
    \texttt{claude-sonnet-4.6} & system under test & closed \\
    \texttt{llama-3.3-70b}     & system under test & open \\
    \bottomrule
  \end{tabular}
  \caption{Models evaluated as the RAG system under test. The item generator is \texttt{claude-sonnet-4.6} and the held-out PCR/validation judge is \texttt{gpt-5} (held out from each other to avoid self-preference); all models are served via OpenRouter.}
  \label{tab:models}
\end{table}

\subsection{Baselines and ablations}
\textbf{Baselines (ladder).} No-RAG (closed-book parametric floor) $\rightarrow$ standard hybrid RAG $\rightarrow$ strong adaptive rivals, Corrective RAG \citep{yan2024crag} and Astute RAG \citep{wang2024astute} (with Self-RAG \citep{asai2024selfrag} as a self-critique reference) $\rightarrow$ oracle gold-passage (correction ceiling). The full ladder runs on single-hop; headline models also run on multi-hop. \textbf{Ablations} (each mapped to a metric): retrieval on/off (isolates parametric vs.\ retrieved correction); corpus noise ratio (gold:distractor:misinfo); prompt (default vs.\ an explicit ``verify the premise'' instruction); and retriever swap (BM25 / dense / hybrid).

\section{Experiments and Results}
\TODO{Full results pending experiment runs. This section will report the metrics below.}

\begin{table}[t]
  \centering
  \small
  \begin{tabular}{lccc}
    \toprule
    \textbf{Setting} & \textbf{PCR} & \textbf{RSR} & \textbf{FP} \\
    \midrule
    Single-hop & \TODO{} & \TODO{} & \TODO{} \\
    Multi-hop  & \TODO{} & \TODO{} & \TODO{} \\
    Agentic    & \TODO{} & \TODO{} & \TODO{} \\
    \bottomrule
  \end{tabular}
  \caption{Premise correction, retrieval sycophancy, and Framing Penalty across architectures (placeholder).}
  \label{tab:main}
\end{table}

\paragraph{H1 (Framing Penalty).} \TODO{Report FP $>0$ with paired McNemar test and CI; expected $\sim$0.10--0.15 correction drop.}
\paragraph{H2 (Retrieval localization).} \TODO{Report RSR and whether premise-confirming retrieval precedes non-correction.}
\paragraph{H3 (Hop amplification).} \TODO{Report HAF; whether multi-hop amplifies FP and agentic recovers.}
\paragraph{H4 (Directional asymmetry).} \TODO{Report within-fact DA and constructibility of both directions.}

\section{Conclusion}
We frame and operationalize a new question for RAG evaluation---whether systems correct corpus-contradicted false premises, and whether ideological framing suppresses correction---and provide a document-grounded pipeline and metric suite (FP, RSR, DA, HAF) to measure it across architectures and models. \TODO{Summarize findings once experiments complete.}

\section*{Limitations}

\paragraph{Synthetic data.} Items are LLM-generated; we mitigate with document grounding, the FEVER lineage, human-$\kappa$ validation, and prompt release, but residual generation artifacts may remain.
\paragraph{Corpus-relative correctness.} ``Correct'' is defined relative to the indexed corpus; for non-FEVER facts we corroborate against external sources (WDI/IMF/UN) and never treat an institution's policy stance as fact, but single-source-of-truth risk persists.
\paragraph{US-centric ideological axis.} The left/right axis is US-centric and may not transfer cross-culturally.
\paragraph{Symmetry is empirical.} Whether congenial falsehoods are equally \emph{constructible} across the political spectrum is an empirical outcome we measure, not an assumption; directional results are conditional on the validated construction and may not generalize beyond it.
\paragraph{Scope.} The agentic setting is a small preview and the international (World Bank) track is left to future work.



\section*{Acknowledgments}

This document has been adapted
by Steven Bethard, Ryan Cotterell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya,
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu,
NAACL 2018 by Margaret Mitchell and Stephanie Lukin,
Bib\TeX{} suggestions for (NA)ACL 2017/2018 from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan,
NAACL 2017 by Margaret Mitchell,
ACL 2012 by Maggie Li and Michael White,
ACL 2010 by Jing-Shin Chang and Philipp Koehn,
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui,
ACL 2005 by Hwee Tou Ng and Kemal Oflazer,
ACL 2002 by Eugene Charniak and Dekang Lin,
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{custom,anthology-overleaf-1,anthology-overleaf-2}

% Custom bibliography entries only
\bibliography{custom}

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

\end{document}
